---
title: "Metadata on the IG monitoring database"
number_sections: yes
output:
  md_document:
    variant: gfm
params:
  pwd: ""
---

Here you'll find a codebook explaining the database structure for the Undressing IG project.

# Setup

Follow the steps below in a terminal to load the database from a dump file and save under the name `igdb`.

```
pg_restore 02-19_backup > backup.sql
sudo -i -u postgres
dropdb igdb
createdb igdb
igdb < backup.sql
```

Load packages needed

```{r}
library("RPostgreSQL")
```

Read database

```{r}
# create a connection to the postgres database
con = dbConnect(dbDriver("PostgreSQL"), dbname= "igdb", host="127.0.0.1", user="postgres", password = params$pwd)

#list tables in the database
dbListTables(con)
```

# Codebook


## data_donors_donor_following


Observed accounts each donor follows

`id`         Pair ID

`donor_id`   Donor ID

`iguser_id`  Observed account ID


## data_donors_datadonation

Log of donation runs

`id`            Encounter ID

`created`       Encounter time

`ig_posts_seen` Number of IG posts seen (12 normally)

`donor_id`      Donor ID


## data_donors_encounter

Log of encounters with posts from observed accounts

`id`                Encounter ID

`position_in_list`  Position of encounter in the user feed. Starts counting at 0

`data_donation_id`  ID of donation run

`ig_post_id`


## data_donors_donor

List of donors

`id`

`ig_donor_id`

`created`

`last_status`

`last_status_changed`

`version`

`updated`

`display_name`


## data_donors_donorfollowing 

List of accounts the donor follows, encountered in the feed during donation runs

`id`

`created`

`following_ig_username`

`donor_id`  


## ig_observer_igimage 

List of images in observed posts

`id`          Image ID

`image_url`   Image URL

`ig_post_id`  Post ID


## ig_observer_iguser 

List of details for observed IG accounts.

`id`                        Account ID

`created`                   Timestamp of observation creation

`ig_username`               Username

`created_by_id`             Observation created by

`ig_biography`              IG Bio

`ig_business_category_name` Business category

`ig_full_name`              Full name

`ig_id`                     IG User ID

`ig_is_business_account`    Is business account?

`ig_profile_pic`            URL of profile pic

`sex`                       Gender of user m or f


## ig_observer_gvisionanalyse 

Result of G Vision analysis

`id`

`analyse`

`ig_image_id`

`created`  


## ig_observer_igpost 

List of posts by observed accounts

`id`                      Post ID

`created`                 Encountered timestamp

`ig_id`                   IG ID

`ig_shortcode`            IG Shortcode

`ig_taken_at_timestamp`   IG picture timestamp

`ig_type`                 Type: Image, Video, Image gallery

`ig_user_id`

`created_by_donor`
