---
title: "Undressing IG: Pre-analysis"
number_sections: yes
output:
  md_document:
    variant: gfm
---

```{r setup}
knitr::opts_knit$set(root.dir = "/home/kira/Nextcloud/Arbeit/AlgorithmWatch/undressing-ig/pre-analysis")
library("needs")
```

# Pre analysis of data

**Goal:** Test the main hypothesis and decide of the opportunity to move from private beta to public beta.

**Tests:** Is the % of 'racy' pictures higher in the feeds of the donors, compared with the % of racy pictures in the items posted by the monitored accounts

## Setup

Follow the steps below in a terminal to load the database from a dump file and save under the name `igdb`.

```
pg_restore 02-19_backup > backup.sql
sudo -i -u postgres
dropdb igdb
createdb igdb
igdb < backup.sql
```

Load packages needed.

```{r warning=FALSE}
needs("RPostgreSQL", "tidyverse", "jsonlite")
```

## Read database

Create variables for the tables from the database needed for this analysis: `data_donors_encounter`, `ig_observer_igimage` and `ig_observer_gvisionanalyse`.

```{r warning=FALSE}
# create a connection to the postgres database
con = dbConnect(dbDriver("PostgreSQL"), dbname= "igdb")

#list tables in the database
dbListTables(con)


# data_donors_encounter: Log of encounters with posts from observed accounts
# "id" "position_in_list "data_donation_id"  "ig_post_id"
data_donors_encounter = dbReadTable(con, "data_donors_encounter")

# ig_observer_igimage: List of images in observed posts
# "id" "image_url" "ig_post_id"  Post ID
ig_observer_igimage = dbReadTable(con, "ig_observer_igimage")

# ig_observer_gvisionanalyse: # Result of G Vision analysis
# "id" "analyse" "ig_image_id" "created"  
ig_observer_gvisionanalyse = dbReadTable(con, "ig_observer_gvisionanalyse")
```

## Stats on current encounters

```{r}
data_donors_encounter %>% nrow %>% cat("encounters total")
(data_donors_encounter$ig_post_id %in% ig_observer_igimage$ig_post_id) %>% ifelse("contains image", "no image") %>% table

data_donors_encounter$ig_post_id %>% unique %>% length %>% cat("unique posts encountered")
(unique(data_donors_encounter$ig_post_id) %in% ig_observer_igimage$ig_post_id) %>% ifelse("contains image", "no image") %>% table

```


## Analysis: Is the share of 'racy' pictures higher in the feeds of the donors than in the items posted by the monitored accounts?

Extract analysis result from G vision JSON blob and save in new column called `racy`.

```{r warning=FALSE}
img = dbReadTable(con, "ig_observer_gvisionanalyse") %>%
  mutate(analyse = sapply(analyse, parse_json),
         racy = sapply(analyse, function(result) result$safeSearchAnnotation$racy) %>% 
           factor(., levels = c("VERY_LIKELY", "LIKELY", "POSSIBLE", "UNLIKELY", "VERY_UNLIKELY"), ordered = TRUE) %>% unname) %>% 
  select(-analyse)
```

Merge sex of IG user to post data

```{r}
sex = dbReadTable(con, "ig_observer_igpost") %>% select(id, ig_user_id) %>%
  left_join(dbReadTable(con, "ig_observer_iguser") %>% select(id, sex), by = c("ig_user_id" = "id"))
```


**Step 1:** Get share of *created* posts containing racy pictures (basis: collected posts by monitored accounts).

```{r}

# take list of posted images (ig_observer_igimage)
x = dbReadTable(con, "ig_observer_igimage") %>%
  # join sex to post ID
  left_join(sex, by = c("ig_post_id" = "id")) %>% 
  # join analysis result to image ID with ig_observer_igimage
  left_join(img, by = c("id" = "ig_image_id"), suffix = c("_ig_img", "_analysis")) %>%
  # summarize by raciness: calculate number and shares of posts
  group_by(sex, racy) %>%
  summarise(n = ig_post_id %>% unique %>% length) %>%
  mutate(share =  n/sum(n))
x
```
- **17%** of posts by women are "very likely" racy, **14%** are "likely" racy.
- **8%** of posts by men are "very likely" racy, **14%** are "likely" racy.

To support our main hypothesis, the shares would need to be higher than this in the encounters logged by data donors.

**Step 2:** Get share of *encountered* posts containing racy pictures (basis: all posts from monitored accounts encountered by donors).

```{r}
# take encounters (data_donors_encounter)
x = dbReadTable(con, "data_donors_encounter") %>% 
# does the post contain a racy image?
  # join sex to post ID
  left_join(sex, by = c("ig_post_id" = "id")) %>% 
  # join image ID to post ID with ig_observer_igimage
  left_join(dbReadTable(con, "ig_observer_igimage") %>% select(-image_url), by = c("ig_post_id"), suffix = c("_encounter", "_ig_img")) %>% 
  # join analysis result to image ID with ig_observer_igimage
  left_join(img, by = c("id_ig_img" = "ig_image_id")) %>% 
  # filter out videos, which have no analysis result
  filter(!is.na(id_ig_img)) %>% 
# how likely is that?
  # summarize by post ID: get highest level of raciness
  group_by(sex, id_encounter, ig_post_id) %>% summarise(racy = min(racy, na.rm = T)) %>% 
  # summarize by raciness: calculate shares
  group_by(sex, racy) %>% summarise(n = n()) %>% mutate(share =  n/sum(n))
x
```

- **20%** of encountered posts by women are "very likely" racy, **12%** are "likely" racy.
- **13%** of encountered posts by men are "very likely" racy, **7%** are "likely" racy.

This does not show a clear picture yet.